The Mysterious Lives Of Speckles. I. Residual atmospheric speckle lifetimes behind AO-fed coronagraphs

### 2021-03-21 specklelives.tex
partial update with some comments from Rus

\citet{2018JATIS...4a9001M} then showed how the residual intensity due to the phase $\Phi$ behind a perfect coronagraph is described by
\begin{equation}
I_\Phi(\vec{r},t) \approx \left(\frac{2\pi}{\lambda}\right)^2 2 \sum_{mn} \left\{  \left[ (h_{mn}^{+})^2 + (h_{mn}^{-})^2 \right] \left[ \Ji^2(\pi D k_{mn}^+) +\Ji^2(\pi D k_{mn}^-)\right] + \mbox{cross-terms} \right\}
\label{eqn:cross_terms}
\end{equation}
where $\Ji$ is the Jinc function
\begin{equation}
\Ji(x) = \frac{\mathrm{J}_1(x)}{x}.
\end{equation}
The cross-terms are a series of terms including products of $h_{mn}^+h_{mn}^-$ and $h_{mn}^ph_{m'n'}^{p'}$ ($mn \neq m'n'$) with $\Ji(x)\Ji(x')$. As long as the aperture truncation is accounted for when the long-exposure statistics are calculated,  these small cross-terms vanish and the long exposure intensity is 
\begin{equation}
\left< I_\Phi(\vec{r}_{mn}) \right> =  \left(\frac{2\pi}{\lambda}\right)^2\left< |h_{mn}|^2 \right> .
\label{eqn:contrast_h2}
\end{equation}
where the discretized position 
\begin{equation}
\vec{r}_{mn} = \vec{k}_{mn} \lambda
\end{equation}
describes the relationship between the spatial-frequency in the pupil plane and projected-angular position in the focal plane.

@@

On the 6.5 m aperture using the SI controller, windspeed has a strong effect, but on the larger ELT scale apertures wind has no significant effect.  We note, that given the range of plausible mean windspeeds, the ELTs are in a different regime of $\mathcal{V} < D$.  That is the crossing time $D/\mathcal{V}$ > 1 s.  Were a mean windspeed significantly higher than 30 m/s to occur, the speckle lifetimes on the ELT will be shorter.

@@

Diameter has a weak effect, with lifetimes dropping as $D$ increases.  When combined as ``crossing time'' $D/V$ there is some evidence for the $\tau \propto D/V$ relation predicted by \citet{2005SPIE.5903..170M} on smaller apertures, but this does not hold for larger telescopes and does not apply to predictive control.

@@

\begin{figure}
\includegraphics[width=5.5in]{scalings.pdf}
\caption{Changes in speckle lifetime with turbulence parameters.  Here absolute spatial frequency is held constant.  The $(m,n)=(10,14)$ mode on the 6.5 m telescope is compared to the $(m,n)=(60,84)$ mode on the 39 m aperture.  This means the input temporal PSD is identical in shape, though the integrated variance changes $\propto D^{-2}$.  Results shown here for turbulence only, without WFS noise. There are few general trends for $D$ and $V$. For the integrator controller there is evidence of a $D/V$ scaling as found by \citet{2005SPIE.5903..170M} up to around $D/V$$\sim$1, however this breaks down on larger apertures and higher winds, and is not evident in predictive control.  Improvement in $r_0$ (larger value, better seeing) shows a general reduction in speckle lifetime in all cases.
\label{fig:scalings}
}
\end{figure}

@@

Here, higher windspeed generally shortens speckle lifetime.  Under SI control, speckle lifetime increases with $D$, but shows little change under LP control.  As $D/V$, we see that there is a scaling up to $D/\mathcal{V} \sim 2$ for the SI, but this breaks down at longer crossing times (slower winds). For the LP controller speckle lifetime is essentially flat vs. $D/\mathcal{V}$.

>>>>

\citet{2018JATIS...4a9001M} then showed how the residual intensity due to the phase $\Phi$ behind a perfect coronagraph is described by
\begin{equation}
I_\Phi(\vec{r},t) \approx \left(\frac{2\pi}{\lambda}\right)^2 2 \sum_{mn} \left\{  \left[ (h_{mn}^{+})^2 + (h_{mn}^{-})^2 \right] \left[ \Ji^2(\pi D k_{mn}^+) +\Ji^2(\pi D k_{mn}^-)\right] + \mbox{cross-terms} \right\}
\label{eqn:cross_terms}
\end{equation}
at location $\vec{r} = r_u \hat{\mathpzc{u}} + r_v\hat{\mathpzc{v}}$. $\Ji$ is the Jinc function
\begin{equation}
\Ji(x) = \frac{\mathrm{J}_1(x)}{x}.
\end{equation}
\jrmadd{and the modified spatial frequencies are given by} 
\begin{eqnarray}
k_{mn}^+ &=& \sqrt{\left(\frac{r_u}{\lambda} + \frac{m}{d}\right) + \left(\frac{r_v}{\lambda} + \frac{n}{d}\right)} \\ 
k_{mn}^- &=& \sqrt{\left(\frac{r_u}{\lambda} - \frac{m}{d}\right) + \left(\frac{r_v}{\lambda} - \frac{n}{d}\right)}. \nonumber
\end{eqnarray}
\jrmadd{Equation \ref{eqn:cross_terms} is equivalent to a convolution with the PSF, adding contributions from nearby speckles.}  The cross-terms are a series of terms including products of $h_{mn}^+h_{mn}^-$ and $h_{mn}^ph_{m'n'}^{p'}$ ($mn \neq m'n'$) with $\Ji(x)\Ji(x')$.  As long as the aperture truncation is accounted for when the long-exposure statistics of $h$ are calculated, the sum can be dropped and these small cross-terms vanish.  The long exposure intensity is 
\begin{equation}
\left< I_\Phi(\vec{r}_{mn}) \right> =  \left(\frac{2\pi}{\lambda}\right)^2\left< |h_{mn}|^2 \right> .
\label{eqn:contrast_h2}
\end{equation}
where the discretized position 
\begin{equation}
\vec{r}_{mn} = \vec{k}_{mn} \lambda
\end{equation}
describes the relationship between the spatial-frequency in the pupil plane and projected-angular position in the focal plane.

@@

On the 6.5 m aperture using the SI controller, windspeed has a strong effect, but on the larger ELT scale apertures wind has no significant effect.  Given the range of plausible mean windspeeds, \jrmadd{the ELTs appear to be in a different regime}.  Were a mean windspeed significantly higher than 30 m/s to occur, the speckle lifetimes on the ELT would be shorter.

@@

Diameter has a weak effect, with lifetimes dropping as $D$ increases.  When combined as ``crossing time'' $D/V$ there is some evidence for the $\tau \propto D/\mathcal{V}$ relation predicted by \citet{2005SPIE.5903..170M} on smaller apertures, but this does not hold for larger telescopes and does not apply to predictive control.

@@

\begin{figure}
\includegraphics[width=5.5in]{scalings.pdf}
\caption{Changes in speckle lifetime with turbulence parameters.  Here absolute spatial frequency is held constant \jrmadd{for all aperture sizes}.  \jrmadd{For instance}, the $(m,n)=(10,14)$ mode on the 6.5 m telescope is compared to the $(m,n)=(60,84)$ mode on the 39 m aperture.   This means the input temporal PSD is identical in shape, though the integrated variance changes $\propto D^{-2}$.  Results shown here for turbulence only, without WFS noise. There are few general trends for $D$ and $V$. For the integrator controller there is evidence of a $D/V$ scaling as found by \citet{2005SPIE.5903..170M} up to around $D/V$$\sim$1, however this breaks down on larger apertures and higher winds, and is not evident in predictive control.  Improvement in $r_0$ (larger value, better seeing) shows a general reduction in speckle lifetime in all cases.
\label{fig:scalings}
}
\end{figure}

@@

Here, higher windspeed generally shortens speckle lifetime.  Under SI control, speckle lifetime increases with $D$, but shows little change under LP control.  There is a scaling up to $D/\mathcal{V} \sim 2$ for the SI, but this breaks down at longer crossing times (slower winds). For the LP controller speckle lifetime is essentially flat vs. $D/\mathcal{V}$.
